### 2021-05-03 newvariant.tex
tweaks

\begin{figure}[!th]
\includegraphics[width=\textwidth]{relspeed.pdf}
\caption{
\textbf{Relative speed of the new variant assuming a fixed strength advantage $\rho$ under five epidemiological conditions.}
The relative speed of the new variant $\delta$ conditional on the strength of the wild type $\Rw$; ratio between the mean generation interval of the new variant $\Gv$ and that of the wild type $\Gw$; and squared coefficient of variation in generation intervals $\kappa$.
Relative speed of the new variant $\delta$ is calculated using $\rho=1.61$, $\Gw = 5\days$, and $\kappa = 1/5$.
Assumed values of $\Rw$ (and therefore $\Rv$) are written on top right corners of each panel.
}
\label{fig:relspeed}
\end{figure}

@@

Even though SARS-CoV-2 has been spreading for more than a year, there is still considerable uncertainty about its generation intervals.
Observational studies typically focus on serial intervals (i.e., time between symptom onset of the infector and the infectee; \cite{svensson2007note}) because they are easier to measure \citep{griffin2020rapid}.
However, realized serial intervals are subject to dynamical biases that can be difficult to tease apart \citep{park2021forward}.
A few studies have tried to estimate the generation-interval distribution from serial intervals, with means ranging between 3--6 days and squared coefficients of variation ranging between 0.1--1 \citep{ferretti2020quantifying,Ferretti2020timing,ganyani2020estimating,knight2020estimating}; 
as we have shown, this uncertainty alone can generate large uncertainty in the inference of relative strength.
Furthermore, most estimates neglect dynamical biases in serial intervals caused by underlying epidemiological dynamics in their estimates of generation intervals.
Serial intervals also fail to account for asymptomatic transmission, adding further uncertainty to inferences of speed and strength \citep{park2020time}.

@@

The spread of new SARS-CoV-2 variants and the replacement of previously dominant lineages represent ongoing challenges for controlling the SARS-CoV-2 pandemic.  
By explicitly considering epidemiological context and generation interval differences together, we have shown that improving estimates of the the relative duration of infectiousness at the individual scale may represent a pathway towards more effective interventions. 
Specifically, we have shown that speed-like interventions, such as contact tracing, will be relatively more effective if variants have longer generation intervals.
Most intervention strategies throughout the current pandemic have focused on strength-like interventions \citep{flaxman2020Rt}, such as lock-downs, partly because pre-symptomatic transmission of SARS-CoV-2 has limited the effectiveness of contact tracing efforts \citep{hellewell2020feasibility}.
However, given the possibility that new variants can have different infection characteristics, future studies should consider whether their transmission dynamics also differ (e.g., the amount of pre-symptomatic transmission) and evaluate intervention strategies accordingly.

@@

\begin{figure}[!pht]
\begin{center}
\includegraphics[width=0.9\textwidth]{Rtbias.pdf}
\caption{
\textbf{Estimates of relative strength over time under different scenarios assuming step changes in reproduction number.}
See Figure 3 of the original text for figure caption.
}
\end{center}
\label{fig:Rtbias}
\end{figure}

>>>>

\begin{figure}[!th]
\includegraphics[width=\textwidth]{relspeed.pdf}
\caption{
\textbf{Relative speed of the new variant assuming a fixed strength advantage $\rho$ under five epidemiological conditions.}
The relative speed of the new variant $\delta$ conditional on the strength of the wild type $\Rw$; ratio between the mean generation interval of the new variant $\Gv$ and that of the wild type $\Gw$; and squared coefficient of variation in generation intervals $\kappa$.
Relative speed of the new variant $\delta$ is calculated using $\rho=1.61$, $\Gw = 5\days$, and $\kappa = 1/5$.
Assumed values of $\Rw$ (and therefore $\Rv$) are shown in the top right corners of each panel.
}
\label{fig:relspeed}
\end{figure}

@@

Even though SARS-CoV-2 has been spreading for more than a year, there is still considerable uncertainty about its generation intervals.
Observational studies typically focus on serial intervals (i.e., time between symptom onset of the infector and the infectee; \cite{svensson2007note}) because they are easier to measure \citep{griffin2020rapid}.
However, realized serial intervals are subject to dynamical biases that can be difficult to tease apart \citep{park2021forward}.
A few studies have tried to estimate the generation-interval distribution from serial intervals, with means ranging between 3--6 days and squared coefficients of variation ranging between 0.1--1 \citep{ferretti2020quantifying,Ferretti2020timing,ganyani2020estimating,knight2020estimating}; 
as we have shown, this uncertainty in the generation-interval distribution alone can generate large uncertainty in the inference of relative strength.
Furthermore, most estimates neglect dynamical biases in serial intervals caused by underlying epidemiological dynamics in their estimates of generation intervals \citep{park2021forward}.
Serial intervals also fail to account for asymptomatic transmission, adding further uncertainty to inferences of speed and strength \citep{park2020time}.

@@

The spread of new SARS-CoV-2 variants and the replacement of previously dominant lineages represent ongoing challenges for controlling the SARS-CoV-2 pandemic \citep{abdool2021new,fontanet2021sars,walensky2021sars}.  
By explicitly considering epidemiological context and generation interval differences together, we have shown that improving estimates of the the relative duration of infectiousness at the individual scale may represent a pathway towards more effective interventions. 
Specifically, we have shown that speed-like interventions, such as contact tracing, will be relatively more effective if variants have longer generation intervals.
Most intervention strategies throughout the current pandemic have focused on strength-like interventions \citep{flaxman2020Rt}, such as lock-downs, partly because pre-symptomatic transmission of SARS-CoV-2 has limited the effectiveness of contact tracing efforts \citep{hellewell2020feasibility}.
However, given the possibility that new variants can have different infection characteristics, future studies should consider whether their transmission dynamics also differ (e.g., the amount of pre-symptomatic transmission) and evaluate intervention strategies accordingly.

@@

\begin{figure}[!pht]
\begin{center}
\includegraphics[width=0.9\textwidth]{Rtbias.pdf}
\caption{
\textbf{Estimates of relative strength over time under different scenarios assuming step changes in reproduction number.}
See Figure 3 of the original text for figure caption.
}
\end{center}
\end{figure}
